### 2014-04-03 paper/exampleobjects.tex
working through comments, now time for george to read

\tovi{Maybe a materials section 
before this - to talk about the 
specific materilas we used, 
such as the copper paint 
specifications, el lighting, etc.
} \valkyrie{I'm not clear on what you are asking for here}

@@

\tovi{go into a bit more detail about modelling , fabrication, and
assembly process, and apparatus details (especially the 
copper paint - unless discussed earlier in a materials 
seciton.}

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in Acoustic Barcodes \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toys}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.

The models we used for the toys' exteriors were all downloaded from the free website Thingiverse.  All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running code by Instructables users DZL and madshobye.

@@

We created a rabbit with a pair of tubes that can simulate breathing (see Figure \ref{fig:breathe}).  For this, we used a combination air/vacuum pump: one terminal creates a vacuum while the other creates positive pressure.  Our rabbit has two tubes, one open tube exiting at its mouth and one semi-closed tube capped with rubberlike material in its abdomen.  We connected one tube to each of our pump's terminals, and using a programmable power supply we can mimic a rabbit's breathing pattern.  This example was printed on our Objet in rubberlike material, with support flushed post-print. \valkyrie{this paragraph is really unclear}

@@

A custom radio built using tubes allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (two potentiometers and a speaker) to a microcontroller (in our case, an Arduino Pro Micro).  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  For the radio functionality, we attached an Si4703 to the Arduino, which offers headphone-jack output.  We fabricated the radio itself on our Makerbot, support-free but cut in two pieces to allow the Arduino and battery pack to be inserted.

@@

We created a maze game with a single particle trapped in a fully enclosed tube.  This maze is based on an SVG we created by hand and processed with our internal path tube tool.  To fabricate the tube, we created it in two halves that were fastened together via glue, due to limitations in our ability to remove support material otherwise.  We created this prototype on our Makerbot in two halves, inserting a marble before closing.

@@

>>>>

@@

In order to demonstrate our star topology feature and show how conductive fluids can be used for touch sensing, we created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in Acoustic Barcodes \cite{Harrison-acoustic}. The objects --- a brain and boat, in our example --- can be set on a base, which announces ``brain'' or ``boat'', and also the names of special features on the object when they are touched. For example, touching the brain model's front protrusion yields the announcement ``olfactory bulb''. The distinct touch points on each object are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toys}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.

The models we used for the toys' exteriors were all downloaded from the free website Thingiverse.  All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing/?ALLSTEPS}

@@

To demonstrate how gases can be used to both provide sensation to the user through openings and to deform a model internally, we created a rabbit with a pair of tubes that can simulate breathing (see Figure \ref{fig:breathe}).  When the rabbit inhales through its nose, its abdomen rises, and as it exhales its abdomen falls.  For this, we used a combination air/vacuum pump: one terminal creates a vacuum while the other creates positive pressure.  Our rabbit has two pipes, one open tube exiting at its mouth and one semi-closed pipe capped with rubberlike material in its abdomen.  We connected one pipe to each of our pump's terminals, and using a programmable power supply we mimic a rabbit's breathing pattern.  This example was printed on our Objet in rubberlike material, with support flushed post-print.

@@

A custom radio, built using pipes integrated with traditional electronics, allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes threaded with wires to connect our components (two potentiometers, an LED, and a speaker) to a microcontroller (Arduino Pro Micro).  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  For the radio functionality, we attached an Si4703 radio tuner breakout board to the Arduino, which offers headphone-jack output.  We fabricated the radio itself on our Makerbot, support-free but cut in two pieces to allow the Arduino and battery pack to be inserted.

@@

@@

Using a modification of our graph-based algorithm which only cuts the literal drawing (and does not perform Eulerization, etc.), we created a maze game with a single particle trapped in a fully enclosed tube.  This maze is based on an SVG we created by hand and processed with our internal path tube tool.  To fabricate the tube, we created it in two halves that were fastened together via glue, due to limitations in our ability to remove support material otherwise. \bjoern{observant reviewers will call us out on this - that many of our techniques may not actually be workable in a single piece because you can't get the support material out. I think if you had a lye bath you could actually get more complicated models done, as long as you're patient and there's some entry and exit for the lye to reach all pipes.}  \valkyrie{we should discuss.  I will try to get a model of this ready ASAP}  We created this prototype on our Objet in two halves, inserting a marble before closing.

### 2014-04-03 paper/tubes.tex
working through comments, now time for george to read

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.pdf}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} and the start and end points highlighted in {\color{gray}gray} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

@@

To avoid the complexities of direct mesh booleans, we construct a discretized volumetric
(ie voxel-based) representation of the original mesh and the tube mesh. Boolean
subtraction is trivial in such representations. We specifically use narrow-band
level sets~\cite{Museth04}, which represent the surface as the zero iso-contour of an
approximate distance field.
We then use marching cubes~\cite{Lorensen87} to produce the final mesh for printing.
This strategy does incur some resampling artifacts, however so does the 3D printing, and compared to the print process, the time required to voxelize at high resolution is inconsequential.
Since we have a distance field, we can easily introduce useful effects, such as the
ability to add a thin membrane "cap" over the end of a tube. 
This is accomplished by applying a standard "thicken" operation to the level set version
of the initial mesh, intersecting with a sphere placed at the tube endpoint, and then performing
a boolean union with the initial shape-minus-tube result.
A straightforward extension would be to add or subtract additional elements at
the tube endpoints to make them non-round.
 \ryan{Figure 8 is not necessary. This is a known problem with any voxelization method. Nobody is going to care that we took shortcuts in our implementation like repeatedly voxelizing and meshing instead of updating a single initial voxelization.}

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.png}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} and the start and end points highlighted in {\color{gray}gray} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

@@

To avoid the complexities of direct mesh booleans, we construct a discretized volumetric
(ie voxel-based) representation of the original mesh and the tube mesh. Boolean
subtraction is trivial in such representations. We specifically use narrow-band
level sets~\cite{Museth04}, which represent the surface as the zero iso-contour of an
approximate distance field.
We then use marching cubes~\cite{Lorensen87} to produce the final mesh for printing.
This strategy does incur some resampling artifacts, however so does the 3D printing, and compared to the print process, the time required to voxelize at high resolution is inconsequential.
Since we have a distance field, we can easily introduce useful effects, such as the
ability to add a thin membrane "cap" over the end of a tube. 
This is accomplished by applying a standard "thicken" operation to the level set version
of the initial mesh, intersecting with a sphere placed at the tube endpoint, and then performing
a boolean union with the initial shape-minus-tube result (see Figure \ref{fig:cap}).
A straightforward extension would be to add or subtract additional elements at
the tube endpoints to make them non-round.
 \ryan{Figure 8 is not necessary. This is a known problem with any voxelization method. Nobody is going to care that we took shortcuts in our implementation like repeatedly voxelizing and meshing instead of updating a single initial voxelization.}

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/cap.pdf}
\caption{The process to ``cap'' the end of a pipe.  In (a), a pipe end is placed on the surface of the mesh.  In (b), we create a sphere whose radius is slightly larger than the radius of the pipe, centred at the tube's endpoint.  In (c), we consider the intersection of the sphere and the pipe, and create an offset surface of the mesh.  Finally, in (d) we intersect with the offset surface.  This is kept as a cap for the pipe in mesh subtraction.}
\label{fig:cap}
\end{figure}
